Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-11 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/ContinuousGeneralisation_Paper_Sigspatial.tex
polished abstract and introduction

\begin{abstract}
We propose a method to continuously 
generalize buildings from a given start scale to a smaller goal scale. 
%
If several buildings are close to each other at the start 
scale, we bridge them by line segments and merge them into 
one 
building.
For each building, either an original one or a merged one, at the start 
scale, 
we generate its target shape at 
the goal scale by enlarging and simplifying. 
Then we grow all buildings to their target shapes.
%
After finishing the growing, we can take the goal scale as the 
start scale and repeat the process.
\newline\indent
The advantages of our method are as follows. First, the buildings 
are enlarged continuously. At the same time, they are simplified. 
Second, we ensure that the distance between any pair of two buildings is 
always larger than a specified threshold.
\end{abstract}

>>>>

\begin{abstract}
We propose a method to continuously 
generalize buildings from a given start map to a smaller-scale goal map.
For the sake of convenience, 
we name the buildings on the start map \emph{original buildings}.
%
For an intermediate scale, 
we aggregate the original buildings that will be too close 
by introducing bridges.
We grow bridged original buildings based on buffering 
and simplify the grown buildings.
We take into account the shapes of the buildings 
both at the previous map and goal map to make sure that 
the buildings are always growing.
%
\newline\indent
The advantages of our method are as follows. 
First, the buildings grow continuously 
and, at the same time, are simplified.
Second, right angles of buildings are preserved during growing. 
Third, the distances between buildings are 
always larger than a specified threshold.
We do a case study to show the performances of our method.
\end{abstract}

### 2017-09-11 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
polished abstract and introduction

Our contributions are as follows.
In \sect\ref{sec:Methodology},
we generalize buildings on a start map to obtain buildings on a goal map.
The generalization consists of aggregating, growing, and simplifying.
We group buildings which will be too close at an output scale.
We aggregate the grouped buildings by introducing bridges.
We grow buildings by buffering,
where we use so-called \emph{miter} joins to keep the right angles of buildings.
Because of using this kind of joins instead of \emph{round} ones,
we have to be more careful.
We show how to solve the problems caused by miter joins.
Eventually, we manage to generate buildings at any intermediate scales.
We carry out a case study in \sect\ref{sec:CaseStudy}
and discuss the performances of our method.
We conclude our paper in \sect\ref{sec:Conclusion}.

@@

We group buildings based on their buffers
(see \fig\ref{fig:RemoveBay} for example).
We wish to remove some ``bays'' 
which have widths less than $2 \dtrm{D}$.
A bay may appear after some buildings are merged by bridging
(see for example \fig\ref{fig:RemoveBay}e).
To remove a such kind of bay,
we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
with distance $\dtrm{D}$.
There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
so we iteratively group until the number of groups does not decrease.
The result of having removed a bay is the outer polygon of 
\fig\ref{fig:RemoveBay}h. 
In comparison, the result is \fig\ref{fig:RemoveBay}e 
if we do not remove a bay.
Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
kind of bay and will be removed by overgrowing.

>>>>

Our contributions are as follows.
In \sect\ref{sec:Methodology},
we generalize buildings on a start map 
to obtain buildings on a smaller-scale goal map.
The generalization consists of aggregating, growing, and simplifying.
We aggregate buildings which will be too close at an output scale 
by introducing bridges.
We grow buildings by buffering,
where we use so-called \emph{miter} joins to keep the right angles of buildings.
Because of using this kind of joins instead of \emph{round} ones,
we have to be more careful.
We show how to solve the problems caused by miter joins.
Eventually, we manage to generate buildings at any intermediate scales.
We carry out a case study in \sect\ref{sec:CaseStudy}
and discuss the performances of our method.
We conclude our paper in \sect\ref{sec:Conclusion}.

@@

We group buildings based on their buffers
(see \fig\ref{fig:RemoveBay} for example).
We wish to remove some ``bays'' 
which have widths less than $2 \dtrm{D}$.
A bay may appear after some buildings are merged by bridging
(see for example \fig\ref{fig:RemoveBay}e).
To remove such kind of bay,
we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
with distance $\dtrm{D}$.
There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
so we iteratively group until the number of groups does not decrease.
The result of having removed a bay is the outer polygon of 
\fig\ref{fig:RemoveBay}h. 
In comparison, the result is \fig\ref{fig:RemoveBay}e 
if we do not remove a bay.
Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
kind of bay and will be removed by overgrowing.
